Human Judgement Forecasting of COVID-19 in the UK

### 2023-03-22 manuscript/manuscript.tex
Updates from Overleaf

On the natural scale, direct forecasts had a slightly better WIS than the Hub ensemble and the other two human forecast ensembles for a two-week-ahead horizon, while the Hub ensemble was again slightly ahead for a four week-ahead horizon (see Figure \ref{fig:performance}). The combined crowd forecast (containing both the direct and the $R_t$ forecasts) overall performed slightly worse than the direct crowd forecast on the natural scale, but much better than the $R_t$ forecasts. On the log scale, the combined crowd forecasts even performed best among the four approaches.

@@

>>>>

On the natural scale, direct forecasts had a better WIS than the Hub ensemble and the other two human forecast ensembles for a two-week-ahead horizon (direct: 34, Hub ensemble: 38, combined crowd: 40, $R_t$: 80), while the Hub ensemble was again slightly ahead for a four week-ahead horizon (direct: 88, Hub ensemble: 85, combined crowd: 98, $R_t$: 150, see Figure \ref{fig:performance} and Table \ref{tab:scores-4}). The combined crowd forecast (containing both the direct and the $R_t$ forecasts) overall performed worse than the direct crowd forecast on the natural scale, but much better than the $R_t$ forecasts. On the log scale, the combined crowd forecasts even performed best among the four approaches.

@@

\input performance-table-horizon-4.tex
